\LARGE \bf Energy-Aware Dynamic Planning Algorithm for Autonomous UAVs

### 2021-01-17 icra-2021.tex
results for fixed plan ready

\begin{figure*}
  \begin{tikzpicture}
    \node[inner sep=0pt] () at (0,7)
        {\footnotesize\input{\figpath/results/trajs_sim3.tikz}};
    \node[inner sep=0pt] () at (0,0)
        {\footnotesize\input{\figpath/results/ener_sim3.tikz}};
    \node[inner sep=0pt] () at (7.9,0)
        {\footnotesize\input{\figpath/results/ener_sim3_detail.tikz}};
  \end{tikzpicture}
  \caption{.}
\end{figure*}

>>>>

\begin{figure*}
  \hspace{-2ex}
  \begin{tikzpicture}
    \node[inner sep=0pt] () at (0,0)
        {\footnotesize\input{\figpath/results/trajs_sim3.tikz}};
    \path[fill=black] (0.0000,0.0000) node[above right] () at (-3,-4) {\footnotesize {(a) path simulation, {\color{red}+} is the UAV location after 200 seconds}};
    \node[inner sep=0pt] () at (8.3,-.02)
        {\footnotesize\input{\figpath/results/ener_sim3.tikz}};
    \path[fill=black] (0.0000,0.0000) node[above right] () at (5.6,-4) {\footnotesize {(b) energy evolution simulation in 200 seconds interval}};
  \end{tikzpicture}
  \caption[Path and energy simulation of a static plan]{Path and energy simulations with different atmospheric conditions. Simulations are performed from collected data by variations of wind speed and direction. The path and computations are static}
  \label{fig:res1}
\end{figure*}
\begin{figure*}
  \begin{tikzpicture}
    \node[inner sep=0pt] () at (6,0)
        {\footnotesize\input{\figpath/results/evol_sim3.tikz}};
    \path[fill=black] (0.0000,0.0000) node[above right] () at (-3.1,-4) {\footnotesize {(a) slice of the simulated energy along the estimated model}};
    \node[inner sep=0pt] () at (10.6,.05)
        {\footnotesize\input{\figpath/results/coef_sim3D.tikz}};
    \path[fill=black] (0.0000,0.0000) node[above right] () at (4.3,-4) {\footnotesize {(b) model evolution at different $k$s}};
    \node[inner sep=0pt] () at (0,0)
        {\footnotesize\input{\figpath/results/ener_sim3_detail.tikz}};
    \path[fill=black] (0.0000,0.0000) node[above right] () at (9.6,-4) {\footnotesize {(c) coefficients evolution}};
  \end{tikzpicture}
  \caption[] {Evolution of the simulated energy data from Figure~\ref{fig:res1}, using the estimation first in~\ref{}, the data with no estimation predicting the future in~\ref{}, and evolution of the estimated coefficients in~\ref{}}
\end{figure*}
